The Adaptive Multi-scale Simulation Infrastructure - Design and Application

### 2016-01-05 doc/articles/amsi_biotissue/paper.tex
working on the paper

\title{The Adaptive Multi-scale Simulation Infrastructure - Design and Implementation of a soft tissue simulation}
\author{W.R. Tobin, D. Fovargue, V.W.L. Chan, M.S. Shephard}
\date{\today}
\documentclass[11pt]{siamltex1213}
\bibliographystyle{siam}

@@

The incremental displacements (the displacement deltas generated by the previous Newton iteration) on each engineering-scale finite element node are used to distort the a dimensionless representative volume element (RVE) resulting in each micro-scale node being displaced. Each RVE is a dimensionless unit cube containing a connected collagen fiber network, for the present results the fibers are implemented as truss elements and their distribution is generated using Delauney triangulation. The micro-scale boundary condition necessitates that the force exerted by each fiber network node located on the boundary of the RVE be zero. The micro-scale global Jacobian is formulated along with the force vector, wherein the boundary condition is enforced by setting specific rows of the force vector associated with boundary nodes to zero.

@@

Thus the simulation as a whole is essentially doubly nonlinear, as during each engineering-scale Newton iteration every micro-scale RVE must undergo a full Newton-Raphson convergence process. 
\section{Results}\label{results}

@@

Work on scale-balancing is ongoing for the Biotissue test problem. Using this work as a basis, a set of algorithms to provide support for more general scale-balancing operations will be developed and packaged into amsi.

>>>>

\title{The Adaptive Multi-scale Simulation Infrastructure - Design and Application}
\author{W.R. Tobin, V.W.L. Chan, M.S. Shephard}
\date{\today}
\documentclass[11pt]{siamltex1213}
\bibliographystyle{siam}

@@

The incremental displacements (deltas generated by the previous Newton-Raphson iteration) on each engineering-scale finite element node are used to distort the a dimensionless representative volume element (RVE) through a dimensionalized abstraction of the RVE embedded in the engineering domain and an associated displacement mapping term $\frac{d\mathbf{RVE}}{d\mathbf{FE}}$, the first order relation between the incremental displacement of an RVE with respect to the displacement of the associated mesh element. This results in each micro-scale node being displaced. Each RVE is a dimensionless unit cube containing a connected collagen fiber network, for the present results the fibers are implemented as truss elements and their distribution is generated using Delauney triangulation. The micro-scale boundary condition necessitates that the force exerted by each fiber network node located on the boundary of the RVE be zero. The micro-scale global Jacobian is formulated along with the force vector, wherein the boundary condition is enforced by setting specific rows of the force vector associated with boundary nodes to zero.

@@

Thus the simulation as a whole is essentially doubly nonlinear, as during each engineering-scale Newton iteration every micro-scale RVE must undergo a full Newton-Raphson convergence process.

\section{Results}\label{results}
The biotissue simulation was run on the AMOS BG/Q machine housed at the CCI facilities. Both strong and weak scaling studies were conducted up to an eighth of the total machine core count, or 16384 cores. The ratio of macro-scale to micro-scale assigned processes was held near 1:128, though the total core count was kept as an integer power of 2 in order for the SLURM job scheduler to submit the jobs to the compute nodes in a timely manner. The precise calculation used to determine macro and micro ratio is given by 
$$ 
num_macro = N 
num_cores = N*128
num_micro = num_cores - N
$$
thus as the number of cores assigned to the macro-scale computation scales, the ratio approaches 1:128.

Separate timings were taken for various sections of the simulation code, isolating the micro-scale computation, macro-scale linear system assembly and calculation of elemental linear systems, and macro-scale linear system solution. In addition, the time for spent in the amsi subroutines for communication was also measured. Thus the behavior of each section of the code is independently evaluated in our scaling study, as well as the overall execution time.

Weak scaling.

Strong scaling.

Amsi-specific results of some sort...?

@@

Work on scale-balancing is ongoing for the biotissue test problem. Using this work as a basis, a set of algorithms to provide support for more general scale-balancing operations will be developed and packaged into amsi.

Scale-sensitive load-balancing operations have been developed for the biotissue multi-scale test problem. Unfortunately the problem does not exhibit load persistence in the current parallel task discretization, so an alternative parallel discretization such as overdecomposition with work-stealing to enforce more local balancing operations and occasional global balancing operations is being explored.
